### 2023-08-11 thesis/sections/4-exp-setup.tex
inlucde architectures

@@

@@

@@

Since with this approach, the model doesn't have any information about the target object, I extend it with a masked image.
As in the section above, a masked version of the image is created and passed to the model.
The model works exactly the same, except for the additional separate image encoder that encodes the masked image in the same way as the original image.
Both encodings are concatenated and then used as the initial hidden state for the LSTM.
This should point the model to which object to describe and discriminate from the other objects.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=.8\linewidth]{figures/discriminator.png}
    \caption{Sender and receiver architectures in the discrimination game}
    \label{fig:discriminator_architecture}
\end{figure}

@@

@@

>>>>

\begin{figure}[h]
    \centering
    \subfigure[Model including one-hot encoded attributes and locations]{
        \includegraphics[width=0.35\linewidth]{figures/arch_coordinate_predictor.png}
        \label{fig:coordinate_predictor_architecture}
    }
    \subfigure[Model including GRE description]{
        \includegraphics[width=0.35\linewidth]{figures/arch_coordinate_predictor_dale.png}
        \label{fig:coordinate_predictor_dale_architecture}
    }
    \caption{Simplified architecture of the coordinate predictors}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=.5\linewidth]{figures/arch_bounding_box_classifier.png}
    \caption{Simplified architecture of the bounding box classifier}
    \label{fig:bounding_box_classifier_architecture}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=.5\linewidth]{figures/arch_caption_generator.png}
    \caption{Simplified architecture of the masked caption generator}
    \label{fig:caption_generator_architecture}
\end{figure}

@@

Since with this approach, the model doesn't have any information about the target object, I extend it with a masked image.
As in the section above, a masked version of the image is created and passed to the model.
This is shown in Figure \ref{fig:caption_generator_architecture}.
The model works exactly the same, except for the additional separate image encoder that encodes the masked image in the same way as the original image.
Both encodings are concatenated and then used as the initial hidden state for the LSTM.
This should point the model to which object to describe and discriminate from the other objects.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=.8\linewidth]{figures/arch_discriminator.png}
    \caption{Sender and receiver architectures in the discrimination game}
    \label{fig:discriminator_architecture}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=.7\linewidth]{figures/arch_caption_generator_game.png}
    \caption{Simplified architecture of the caption generator game}
    \label{fig:caption_generator_game_architecture}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=.7\linewidth]{figures/arch_coordinate_predictor_game.png}
    \caption{Simplified architecture of the masked coordinate predictor game}
    \label{fig:coordinate_predictor_game_architecture}
\end{figure}
